---
title: "Department profiles"
---

```{r global-options, include=FALSE}
# Set echo=false for all chunks
knitr::opts_chunk$set(echo=FALSE)
```


This is a draft document. 

Please note all data presented here are provisional and intended only for feedback purposes. It is possible that the figures presented here will change in future. 

While any changes to the data are not likely to be substantial, we are planning to carry out more in-depth analysis and the commentary may change. As such, we recommend linking to these pages rather than sharing this analysis any other way at this stage. We will be regularly updating these pages with additional outputs and insights. 

Below are links to department-specific profiles. These contain the outputs present on the summary statistics page, filtered by department. Only departments with 20 or more respondents are included.

## Department sample sizes

``` {r}

library(magrittr)

if(!exists("data")) stop("Dataframe called data not available. This should be in the 
                                      function enviroment of render_main_site. Check that this is available in this
                                      enviroment.")

dep_freqs <- data.frame(table(data$department))
dep_freqs <- dep_freqs[dep_freqs[2] >= 20, ]
dep_freqs[1] <- as.character(dep_freqs[[1]])
colnames(dep_freqs) <- c("Department", "Sample size")

```

``` {r}

dep_freqs_plot <- dep_freqs
dep_freqs_plot[1] <- stringr::str_wrap(dep_freqs_plot[[1]], width = 40)
dep_freqs_plot[1] <- gsub("\\n", "<br>", dep_freqs_plot[[1]])
dep_freqs_plot <- dep_freqs_plot[(order(dep_freqs_plot[1])), ]
dep_freqs_plot[1] <- factor(dep_freqs_plot[[1]], levels = dep_freqs_plot[[1]])

plot <- carsurvey2::plot_freqs(dep_freqs_plot, "", "Sample size", n = samples$all, font_size = 14, orientation = "h", width = 700, height = 1000)

table <- kableExtra::kable_styling(knitr::kable(dep_freqs_plot, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("dep-freqs", plot, table)

```


``` {r}

department <- data.frame(table(data$department))
dep_list <- department[department[2] >= 20, ]

alphabetical <- as.character(dep_list$Var1[order(dep_list[[1]])])
urls <- carsurvey2::format_filter_path(alphabetical)
links <- paste0('<li><a href="Department/', urls, '.html">', alphabetical, "</a></li>")
html <- paste(links, collapse="\n\n")
html <- paste0("<ol>", html, "</ol>")
knitr::raw_html(html)

```
