---
title: "Analytical profession profiles"
---

```{r global-options, include=FALSE}
# Set echo=false for all chunks
knitr::opts_chunk$set(echo=FALSE)
```

Please note it is possible that the figures presented here will change in future. 

While any changes to the data are not likely to be substantial, we are planning to carry out more in-depth analysis and the commentary may change. As such, we recommend linking to these pages rather than sharing this analysis any other way at this stage. We will be regularly updating these pages with additional outputs and insights. 

Below are links to profession-specific profiles. These contain the outputs present on the summary statistics page, filtered by profession. Only professions with 20 or more respondents are included.

## Profession sample sizes

``` {r}

library(magrittr)

if(!exists("data")) stop("Dataframe called data not available. This should be in the function enviroment of render_main_site. Check that this is available in this enviroment.")

data$prof_DS <- ifelse(data$prof_DS_GSG_GORS == "Yes" | data$prof_DS_other == "Yes", "Yes", "No"
                       )
profs <- dplyr::select(data, prof_non_CS, prof_DDAT:prof_none_CS, prof_DS)
prof_freqs <- carsurvey2::calc_multi_col_freqs(profs, c("Yes", "No"))
prof_freqs <- prof_freqs[c(1,2)]

prof_freqs <- prof_freqs[prof_freqs[2] >= 20, ]
prof_freqs[1] <- as.character(prof_freqs[[1]])
colnames(prof_freqs) <- c("Profession", "Sample size")

recode_vals <- c(
  prof_non_CS = "Non-Civil Service",
  prof_DS = "Government Data Scientist",
  prof_DDAT = "Digital, Data and Technology Profession",
  prof_GAD = "Government Actuarial Profession",
  prof_GES = "Government Economic Service",
  prof_finance = "Government Finance Profession",
  prof_geography = "Government Geography Profession",
  prof_GORS = "Government Operational Research Service",
  prof_GSR = "Government Social Research",
  prof_GSG = "Government Statistician Group",
  prof_none_CS = "Civil Service, no profession membership"
  )

prof_freqs$Profession <- dplyr::recode(prof_freqs$Profession, !!!recode_vals)

```

``` {r}

plot_freqs <- prof_freqs
plot_freqs$Profession <- carsurvey2::break_q_names(prof_freqs$Profession)
plot <- carsurvey2::plot_freqs(plot_freqs, "", "Sample size", font_size = 14, n = samples$all, orientation = "h", width = 700, height = 700)

table <- kableExtra::kable_styling(knitr::kable(prof_freqs, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("prof-freqs", plot, table)

```

``` {r}

alphabetical <- as.character(prof_freqs$Profession[order(prof_freqs$Profession)])
urls <- carsurvey2::format_filter_path(alphabetical)
links <- paste0('<li><a href="profession/', urls, '.html">', alphabetical, "</a></li>")
html <- paste(links, collapse="\n\n")
html <- paste0("<ol>", html, "</ol>")
knitr::raw_html(html)

```

