---
title: "Summary statistics"
output:
  html_document:
    toc: true
    toc_depth: 1
    toc_float: 
      collapsed: false
---

```{r global-options, include=FALSE}
# Set echo=FALSE for all chunks
knitr::opts_chunk$set(echo=FALSE)

library(magrittr)

tables <- carsurvey3::summarise_all(data)

```

This is a draft document. 

Please note all data presented here are provisional and intended only for feedback purposes. It is possible that the figures presented here will change in future. 

While any changes to the data are not likely to be substantial, we are planning to carry out more in-depth analysis and the commentary may change. As such, we recommend referring to these pages rather than sharing this analysis any other way at this stage. We will be regularly updating these pages with additional outputs and insights. 

# Coding frequency and tools

## Most respondents use code at least regularly in their current role

Over half of respondents reported using code to achieve their work objectives regularly or all the time. This survey is likely to have attracted many analysts with an interest in programming, meaning these figures may be skewed. Nevertheless, the figures here show that for many government analysts programming has become a key tool in their work.

```{r}
plot <- carsurvey2::plot_freqs(tables$code_freq, "Coding frequency", "Count", n = samples$all, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$code_freq)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("coding-freq", plot, table)

```

## Respondents use code to perform a variety of data operations 

Most respondents use code to perform each of the data operations included in the survey, at least in part. While these were the responses to the questions included, many respondents reported other data operations in the free text box provided. Code is currently being used in government at every stage of analysis pipelines, from pre-processing through to analysis and presentation. 

```{r}
plot <- carsurvey2::plot_stacked(tables$operations, "Count", "Data operation", n = samples$all, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$operations)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("operations", plot, table)
```


## Access to and knowledge of programming languages

Given a list of programming tools, we asked respondents to answer “Yes”, “No” or “Don’t know” for the following statements;

* This tool is available to use for my work.
* I know how to program with this tool to a level suitable for my work. 

Please note we did not set precise definitions for availability and knowledge here, as these are dependent on individual circumstances. 


## Open source tools are the most available for analysts work

R, SQL and Python were the three most available programming languages to government analysts. All three are open source languages, the use of which is a key component of the [RAP methodology](https://gss.civilservice.gov.uk/reproducible-analytical-pipelines/). Such tools help analysts make their work more transparent and reproducible to their users, as cost is not a barrier to use. 

```{r}
plot <- carsurvey2::plot_stacked(tables$access, xlab = "Count", ylab = "Programming tool", n = samples$all, colour_scale = "3scale", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$access, row.names = FALSE)) %>%  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-access", plot, table)
```

## Capability is most common in open-source tools

More respondents said they were able to carry out their work using Python, SQL and R, showing open-source tools also lead the way in capability. 

```{r}
plot <- carsurvey2::plot_stacked(tables$knowledge, xlab = "Count", ylab = "Programming tool", n = samples$all, colour_scale = "3scale", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$knowledge, row.names = FALSE)) %>%  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-knowledge", plot, table)
```

## Access and knowledge gaps

Using data collected from previous questions we calculated the number of respondents who have access but no knowledge, access and knowledge, and knowledge but no access for each programming language. 

## Many respondents have capability in tools they cannot access in work

A large minority of respondents have capability in programming languages they do not have access to. This is particularly true for proprietary software. A further advantage of open-source software is that it is easier for analysts' coding skills to be transferable if they learn an open-source language, as they are more likely to have access to the same software at another department in future.


```{r}

plot <- carsurvey2::plot_stacked(tables$language_status, colour_scale = "3scale", xlab = "Count", ylab = "Programming tool", n = samples$all, font_size = 14, width = 700)

table <- kableExtra::kable_styling(knitr::kable(tables$language_status, row.names = FALSE)) %>%
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-status", plot, table)

```


# Coding capability

## Most analysts said their coding ability has improved during current role

Responses show many analysts in government are either maintaining or actively improving their coding capability. But this is not true across the board. A large minority reported a decrease in their coding abilities in their current role. 

This question was only asked of respondents with coding experience outside of their current role. This means the data does not cover those who first learned to code in their current role.


``` {r}
plot <- carsurvey2::plot_freqs(tables$ability_change, xlab = "Change in ability", ylab = "Count", n = samples$code_outside_current_role, break_q_names_col = "Ability Change", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$ability_change, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$code_outside_current_role))

carsurvey2::wrap_outputs("ability", plot, table)

```

## Most respondents learned to code outside of the public sector

Analysts are generally learning to code for the first time before joining the public sector, particularly in education. However, many reported learning to code for the first time in their current role or in previous public sector employment. This shows that not only are analysts with previous coding experience improving, but those without those skills are being upskilled as well.


``` {r}

plot <- carsurvey2::plot_freqs(tables$where_learned, xlab = "", ylab = "Count", n = samples$any_code_experience, break_q_names_col = "First coding experience", orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$where_learned, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$any_code_experience))

carsurvey2::wrap_outputs("first-learn", plot, table)

```


# Coding practices

We asked respondents who said they use code in their work how often they carry out various coding practices considered to be good practice. For more information on the practices presented below, please read our guidance on [quality assurance of code for analysis and research](https://best-practice-and-impact.github.io/qa-of-code-guidance/intro.html).

## Many good coding practices are not regularly applied by analysts

Most respondents reporting using these practices at least some of the time, but often not regularly. It appears many analysts have the skills to use these practices, but either do not have time or do not feel the need to do so. However, all these practices are intended to improve the reproducibility, assurance and auditability of code.

```{r}
plot <- carsurvey2::plot_likert(tables$coding_practices, 5, "Frequency", "", n = samples$coders, neutral_mid = FALSE, font_size = 14, height = 1200, width = 700, break_q_names_col = "Question", max_lines = 3)

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$coding_practices)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("code-prac", plot, table)

```


## Most types of documentation are not regularly used

Similarly, most respondents do not write most forms of code documentation regularly, with the exception of code comments. 

[Embedded documentation](https://best-practice-and-impact.github.io/qa-of-code-guidance/code_documentation.html) is one of the components which make up a RAP minimum viable product. Documentation is important to help others be clear on what the code is doing.


```{r}
plot <- carsurvey2::plot_likert(tables$doc, 5, "Frequency", "", n = samples$coders, neutral_mid = FALSE, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$doc)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("doc", plot, table)

```

## A minority are using dependency management or reproducible workflow packages

More advanced coding practices are less common still, with only a minority carrying them out at all. 

```{r}

plot <- carsurvey2::plot_freqs(tables$dependency_management, xlab = "Use dependency management software", ylab = "count", n = samples$coders, break_q_names_col = "Use dependency management software", font_size = 14, width = 600)


table <- kableExtra::kable_styling(knitr::kable(tables$dependency_management)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("dep_management", plot, table)

```




```{r}

plot <- carsurvey2::plot_freqs(tables$rep_workflow, xlab = "Use reproducible workflows packages", ylab = "count", n = samples$coders, break_q_names_col = "Use reproducible workflow packages", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rep_workflow)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("workflow", plot, table)

```


# RAP knowledge and opinions

We asked respondents about their knowledge of and opinions on [reproducible analytical pipelines (RAP)](https://gss.civilservice.gov.uk/reproducible-analytical-pipelines/). RAP refers to the use of practices from software engineering to make analysis more reproducible. These practices build on the advantages of writing analysis as code by ensuring increased quality, trust, efficiency, business continuity and knowledge management. The [RAP champions](https://gss.civilservice.gov.uk/about-us/champion-networks/reproducible-analytical-pipeline-rap-champions/) are a network of analysts across government who promote and support RAP development in their departments.

# Most respondents have heard of RAP

65% of respondents have heard of RAP which means a large minority haven’t heard of RAP and its principles. RAP and its principles are considered best practice and help to improve analysis. If respondents haven’t heard of RAP it means these best practices are less likely to be implemented.


```{r}
plot <- carsurvey2::plot_freqs(tables$rap_knowledge, "", "Count", n = samples$all, font_size = 14, orientation = "h", break_q_names_col = "RAP champion knowledge", max_lines = 3, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rap_knowledge, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("rap-knowledge", plot, table)

```


## Respondents are positive about RAP knowledge and implementation

We asked respondents who had heard of RAP whether they agreed with a series of statements.

```{r}
plot <- carsurvey2::plot_likert(tables$rap_opinions, 3, "Frequency", "", n = samples$heard_of_rap, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$rap_opinions)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$heard_of_rap))

carsurvey2::wrap_outputs("rap-opinions", plot, table)

```


# RAP scores

## Some components of RAP are not implemented often

From the responses, you can see the least common practice is open sourcing code. This is required to meet the [minimum viable product](https://gss.civilservice.gov.uk/reproducible-analytical-pipelines/) and as we have so few respondents reporting doing it that means we don’t have many products currently being produced which meet MVP even with the other components higher use. 

The frequencies for each RAP component are derived where respondents answered “regularly” or “all the time” to the relevant questions. This graph shows the frequency of basic and advanced RAP components. “Basic” relates to the components which make up MVP. Advanced are practices which although not compulsory for MVP we highly recommend are done for good practice. 


```{r}
plot <- carsurvey2::plot_grouped(tables$rap_components, "", "Count", n = samples$coders, orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rap_components, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("rap_comps", plot, table)

```


## Very few respondents are regularly meeting RAP MVP standards

While 49% of respondents say they feel comfortable implementing RAP only 2% respondents are regularly meeting RAP MVP. A large minority of responses are completing none of the basic RAP principles with 92% of respondents have a basic RAP score of 3 or less.

To calculate a respondent's basic RAP score sum each of the basic RAP components used regularly.

```{r}

bar_colour <- carsurvey2::get_2colour_scale(2)[2][[1]]
bar_colour <- rgb(bar_colour[1],bar_colour[2],bar_colour[3], maxColorValue = 255)

plot <- carsurvey2::plot_freqs(tables$basic_rap_scores, "Basic RAP score", "Count", bar_colour = bar_colour, n = samples$coders, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$basic_rap_scores, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("basic_score", plot, table)

```


## Few respondents regularly use multiple advanced RAP components

To calculate a respondent's advanced RAP score sum each of the advanced RAP components used regularly.

```{r}

plot <- carsurvey2::plot_freqs(tables$advanced_rap_scores, "Advanced RAP score", "Count", n = samples$coders, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$advanced_rap_scores, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("advanced_score", plot, table)

```
