---
title: "Summary statistics"
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
---

```{r global-options, include=FALSE}
# Set echo=FALSE for all chunks
knitr::opts_chunk$set(echo=FALSE)

library(magrittr)

tables <- carsurvey3::summarise_all(data)

```


This is a draft document. 

Please note all data presented here are provisional and intended only for feedback purposes. It is possible that the figures presented here will change in future. 


# Coding frequency and tools


## Most respondents use code at least regularly in their current role

Over half of our respondents say they code either regularly or all the time in their current role. 

Please note a key network for advertising this survey was through our RAP champions. This may cause the data may skew towards more frequent coders. This sample may not be representative of all analysts across government.


```{r}
plot <- carsurvey2::plot_freqs(tables$code_freq, "Coding frequency", "Count", n = samples$all, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$code_freq)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("coding-freq", plot, table)

```

## Respondents preform a variety of data operations with code

For the given list of data operations, the majority of respondents complete them all using at least some code.

The question was only concerned with if people use code at all to complete data operations. This could mean a small amount is done by code and this response would still be selected. 

```{r}
plot <- carsurvey2::plot_stacked(tables$operations, "Count", "Data operation", n = samples$all, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$operations)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("operations", plot, table)
```



## Access to and knowledge of programming languages

Given a list of programming tools, we asked respondents to answer “Yes”, “No” or “Don’t know” for the following statements;

* This tool is available to use for my work.
* I know how to program with this tool to a level suitable for my work. 


## Open source tools are the most available for analysts work

The three most available coding tools are all open source; R, SQL and Python respectively. Proprietary tools like SPSS and SAS are still commonly available to analysts. There is also more uncertainty around access to proprietary tools.

We allowed for the respondents to have their own definition of access for this question. 

```{r}
plot <- carsurvey2::plot_stacked(tables$access, xlab = "Count", ylab = "Programming tool", n = samples$all, colour_scale = "3scale", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$access, row.names = FALSE)) %>%  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-access", plot, table)
```

## Capability is most common in open source tools

More respondents said they were able to carry out their work using open source tools. There is still some common propriety software capability. 

The questions asked if people had enough experience in the tool to produce work which was at an acceptable level. The definition of an acceptable level was left up to the respondent to decide.



```{r}
plot <- carsurvey2::plot_stacked(tables$knowledge, xlab = "Count", ylab = "Programming tool", n = samples$all, colour_scale = "3scale", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$knowledge, row.names = FALSE)) %>%  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-knowledge", plot, table)
```

## Access and knowledge gaps

Using data collected from previous questions we calculated the number of respondents who have access but no knowledge, access and knowledge, and knowledge but no access for each programming language. 

## Many respondents have capability in tools they cannot access in work

Many respondents have knowledge of programming tools which they can use in their work especially for proprietary tools. There are also respondents who have knowledge of Python but no way of accessing. Python has no cost associated unlike proprietary tools.  

```{r}

plot <- carsurvey2::plot_stacked(tables$language_status, colour_scale = "3scale", xlab = "Count", ylab = "Programming tool", n = samples$all, font_size = 14, width = 700)

table <- kableExtra::kable_styling(knitr::kable(tables$language_status, row.names = FALSE)) %>%
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-status", plot, table)

```


# Coding capability

## Change in coding ability during current role

``` {r}
plot <- carsurvey2::plot_freqs(tables$ability_change, xlab = "Change in ability", ylab = "Count", n = samples$code_outside_current_role, break_q_names_col = "Ability Change", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$ability_change, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$code_outside_current_role))

carsurvey2::wrap_outputs("ability", plot, table)

```

## Where respondents learned to code

Respondents were asked whether they had coding experience outside their current role and, if so, where. Most of the respondents first learnt code in education.

``` {r}

plot <- carsurvey2::plot_freqs(tables$where_learned, xlab = "", ylab = "Count", n = samples$any_code_experience, break_q_names_col = "First coding experience", orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$where_learned, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$any_code_experience))

carsurvey2::wrap_outputs("first-learn", plot, table)

```


# Coding practices


## General coding practices

```{r}
plot <- carsurvey2::plot_likert(tables$coding_practices, 5, "Frequency", "", n = samples$coders, neutral_mid = FALSE, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$coding_practices)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("code-prac", plot, table)

```


## Documentation


```{r}
plot <- carsurvey2::plot_likert(tables$doc, 5, "Frequency", "", n = samples$coders, neutral_mid = FALSE, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$doc)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("doc", plot, table)

```

## Dependency management

```{r}

plot <- carsurvey2::plot_freqs(tables$dependency_management, xlab = "Use dependency management software", ylab = "count", n = samples$coders, break_q_names_col = "Use dependency management software", font_size = 14, width = 600)


table <- kableExtra::kable_styling(knitr::kable(tables$dependency_management)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("dep_management", plot, table)

```


## Reproducible workflow packages


```{r}

plot <- carsurvey2::plot_freqs(tables$rep_workflow, xlab = "Use reproducible workflows packages", ylab = "count", n = samples$coders, break_q_names_col = "Use reproducible workflow packages", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rep_workflow)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("workflow", plot, table)

```


# RAP knowledge and opinions

# Knowledge of RAP

```{r}
plot <- carsurvey2::plot_freqs(tables$rap_knowledge, "", "Count", n = samples$all, font_size = 14, orientation = "h", break_q_names_col = "RAP champion knowledge", max_lines = 3, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rap_knowledge, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("rap-knowledge", plot, table)

```


## Opinions on RAP

```{r}
plot <- carsurvey2::plot_likert(tables$rap_opinions, 3, "Frequency", "", n = samples$heard_of_rap, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$rap_opinions)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$heard_of_rap))

carsurvey2::wrap_outputs("rap-opinions", plot, table)

```


# RAP scores

## RAP components

```{r}
plot <- carsurvey2::plot_grouped(tables$rap_components, "", "Count", n = samples$coders, orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rap_components, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("rap_comps", plot, table)

```


## Basic RAP scores

```{r}

bar_colour <- carsurvey2::get_2colour_scale(2)[2][[1]]
bar_colour <- rgb(bar_colour[1],bar_colour[2],bar_colour[3], maxColorValue = 255)

plot <- carsurvey2::plot_freqs(tables$basic_rap_scores, "Basic RAP score", "Count", bar_colour = bar_colour, n = samples$coders, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$basic_rap_scores, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("basic_score", plot, table)

```


## Advanced RAP scores

```{r}

plot <- carsurvey2::plot_freqs(tables$advanced_rap_scores, "Advanced RAP score", "Count", n = samples$coders, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$advanced_rap_scores, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("advanced_score", plot, table)

```
