---
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
params: 
  title: "Default"
title: "`r params$title`"
---

```{r global-options, include=FALSE}
# Set echo=FALSE for all chunks
knitr::opts_chunk$set(echo=FALSE)

library(magrittr)

tables <- carsurvey3::summarise_all(filtered_data)

```

This is a living document. We want our users to get as much value as possible from our analysis. Because of that, we will be updating these pages with additional outputs and insights when possible. To make sure you always access the latest insights, we recommend linking to these pages rather than sharing this analysis any other way at this stage. 

# Coding frequency and tools

## Coding frequency

We asked respondents "In your current role, how often do you write code to complete your work objectives?".

```{r}
plot <- carsurvey2::plot_freqs(tables$code_freq, "Coding frequency", "Count", n = samples$all, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$code_freq)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("coding-freq", plot, table)

```
<br>

## What people are using code for 

We asked respondents what data operations they carry out in their work, and whether they use code to do them. Please note we did not ask how much of each data operation is done with code, or how often.  

```{r}
plot <- carsurvey2::plot_stacked(tables$operations, "Count", "Data operation", n = samples$all, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$operations)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("operations", plot, table)
```
<br>

## Access to and knowledge of programming languages

Given a list of programming tools, we asked respondents to answer “Yes”, “No” or “Don’t know” for the following statements;

* This tool is available to use for my work.
* I know how to program with this tool to a level suitable for my work. 

Access to tools does not necessarily refer to official policy. Some analysts may have access to tools others cannot access within the same organisation. 

Please note that capability in programming languages is self-reported here and was not objectively defined or tested.

<br> 

## Access to coding tools

```{r}
plot <- carsurvey2::plot_stacked(tables$access, xlab = "Count", ylab = "Programming tool", n = samples$all, colour_scale = "3scale", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$access, row.names = FALSE)) %>%  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-access", plot, table)
```
<br>

## Knowledge of coding tools

```{r}
plot <- carsurvey2::plot_stacked(tables$knowledge, xlab = "Count", ylab = "Programming tool", n = samples$all, colour_scale = "3scale", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$knowledge, row.names = FALSE)) %>%  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-knowledge", plot, table)
```
<br>

## Access and knowledge gaps

Using the data presented above we calculated the number of respondents with:

* Access to tools they do not have the capability to use (access only),
* Access to tools they are able to use (access and knowledge)
* Or capability to use tools they cannot access at work (knowledge only)

```{r}

plot <- carsurvey2::plot_stacked(tables$language_status, colour_scale = "3scale", xlab = "Count", ylab = "Programming tool", n = samples$all, font_size = 14, width = 700)

table <- kableExtra::kable_styling(knitr::kable(tables$language_status, row.names = FALSE)) %>%
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-status", plot, table)

```


# Coding capability

<br>

## Change in coding ability during current role

This question was only asked of respondents with coding experience outside of their current role. This means analysts who first learned to code in their current role are not included in the data.

``` {r}
plot <- carsurvey2::plot_freqs(tables$ability_change, xlab = "Change in ability", ylab = "Count", n = samples$code_outside_current_role, break_q_names_col = "Ability Change", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$ability_change, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$code_outside_current_role))

carsurvey2::wrap_outputs("ability", plot, table)

```
<br>

## Where respondents first learned to code

Respondents with coding experience outside their current role were asked when they first learned to code. This output also includes analysts who code in their current role but reported no other coding experience.

These data only show where people first learned to code. They do not show all the settings in which they had learned to code, to what extent, or how long ago.


``` {r}

plot <- carsurvey2::plot_freqs(tables$where_learned, xlab = "", ylab = "Count", n = samples$any_code_experience, break_q_names_col = "First coding experience", orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$where_learned, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$any_code_experience))

carsurvey2::wrap_outputs("first-learn", plot, table)

```
<br>

# Coding practices

We asked respondents who said they currently use code in their work how often they carry out various coding practices. For more information on the practices presented below, please read our guidance on [Quality Assurance of Code for Analysis and Research](https://best-practice-and-impact.github.io/qa-of-code-guidance/intro.html).

## General coding practices

```{r}
plot <- carsurvey2::plot_likert(tables$coding_practices, 5, "Frequency", "", n = samples$coders, neutral_mid = FALSE, font_size = 14, height = 1200, width = 700, break_q_names_col = "Question", max_lines = 3)

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$coding_practices)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("code-prac", plot, table)

```
<br>

## Documentation

[Embedded documentation](https://best-practice-and-impact.github.io/qa-of-code-guidance/code_documentation.html) is one of the components which make up a RAP minimum viable product. Documentation is important to help others be clear on how to use the product and what the code is intended to do. 

```{r}
plot <- carsurvey2::plot_likert(tables$doc, 5, "Frequency", "", n = samples$coders, neutral_mid = FALSE, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$doc)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("doc", plot, table)

```
<br>

## Dependency management

Respondents who currently use code in their work were asked whether they use any tools for dependency management. We provided examples of tools that may be used for dependency management: 

* Requirements files, e.g. python requirements.txt or R DESCRIPTION files
* Virtual environments (e.g. venv or renv) or virtual machines
* Containers e.g. Docker

```{r}

plot <- carsurvey2::plot_freqs(tables$dependency_management, xlab = "Use dependency management software", ylab = "count", n = samples$coders, break_q_names_col = "Use dependency management software", font_size = 14, width = 600)


table <- kableExtra::kable_styling(knitr::kable(tables$dependency_management)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("dep_management", plot, table)

```

<br>

## Reproducible workflow packages

Respondents were asked whether they use continuous integration technologies. As above, respondents were provided with examples of what those might be: 

* GitHub actions
* Jenkins
* Travis

``` {r}

plot <- carsurvey2::plot_freqs(tables$rep_workflow, xlab = "Use reproducible workflows packages", ylab = "count", n = samples$coders, break_q_names_col = "Use reproducible workflow packages", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rep_workflow)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("workflow", plot, table)

```
<br>

# RAP knowledge and opinions

We asked respondents about their knowledge of and opinions on [reproducible analytical pipelines (RAP)](https://gss.civilservice.gov.uk/reproducible-analytical-pipelines/). RAP refers to the use of practices from software engineering to make analysis more reproducible. These practices build on the advantages of writing analysis as code by ensuring increased quality, trust, efficiency, business continuity and knowledge management. The [RAP champions](https://gss.civilservice.gov.uk/about-us/champion-networks/reproducible-analytical-pipeline-rap-champions/) are a network of analysts across government who promote and support RAP development in their departments.

<br>

# Knowledge of RAP

We asked our respondents whether they had heard of RAP and what their knowledge is of their own department RAP champion.

```{r}
plot <- carsurvey2::plot_freqs(tables$rap_knowledge, "", "Count", n = samples$all, font_size = 14, orientation = "h", break_q_names_col = "RAP champion knowledge", max_lines = 3, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rap_knowledge, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("rap-knowledge", plot, table)

```
<br>

```{r}
## line manage

plot <- carsurvey2::plot_freqs(tables$line_manage, xlab = "", ylab = "Count", n = samples$all, break_q_names_col = "Line manage anyone who writes codes", orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$line_manage, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("line-manage", plot, table)

```
<br>

## Opinions on RAP

We asked respondents who had heard of RAP whether they agreed with a series of statements.

```{r}
plot <- carsurvey2::plot_likert(tables$rap_opinions, 3, "Frequency", "", n = samples$heard_of_rap, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$rap_opinions)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$heard_of_rap))

carsurvey2::wrap_outputs("rap-opinions", plot, table)

```
<br>

# RAP scores

RAP component scores “regularly” or “all the time” to the relevant questions. For documentation, this includes both code comments and README files. For the continuous integration and dependency management components we only collected "yes", "no" or "I don't understand the question" responses. As such, we gave "yes" responses a score of 1. The sum total of each respondent's scores is presented here as "RAP scores". 

A score of one for each RAP component is derived where respondents answered “regularly” or “all the time” to the relevant questions. For documentation, this includes both code comments and README files. For the continuous integration and dependency management components we only collected "yes", "no" or "I don't understand the question" responses. As such, we gave "yes" responses a score of 1. The sum total of each respondent's scores is presented here as "RAP scores". “Basic components” are the components which make up the RAP MVP. "Advanced components" are components that help improve reproducibility, but were are considered part of the minimum standard. 

<br>

## RAP components


```{r}
plot <- carsurvey2::plot_grouped(tables$rap_components, "", "Count", n = samples$coders, orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rap_components, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("rap_comps", plot, table)

```
<br>

## Basic RAP scores

```{r}

bar_colour <- carsurvey2::get_2colour_scale(2)[2][[1]]
bar_colour <- rgb(bar_colour[1],bar_colour[2],bar_colour[3], maxColorValue = 255)

plot <- carsurvey2::plot_freqs(tables$basic_rap_scores, "Basic RAP score", "Count", bar_colour = bar_colour, n = samples$coders, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$basic_rap_scores, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("basic_score", plot, table)

```
<br>

## Advanced RAP scores

```{r}

plot <- carsurvey2::plot_freqs(tables$advanced_rap_scores, "Advanced RAP score", "Count", n = samples$coders, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$advanced_rap_scores, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("advanced_score", plot, table)

```

