---
output:
  html_document:
    toc: true
    toc_depth: 2
    toc_float: 
      collapsed: false
params: 
  title: "Default"
title: "`r params$title`"
---

```{r global-options, include=FALSE}
# Set echo=FALSE for all chunks
knitr::opts_chunk$set(echo=FALSE)

library(magrittr)

tables <- carsurvey3::summarise_all(filtered_data)

```

This is a draft document. 

Please note all data presented here are provisional and intended only for feedback purposes. It is possible that the figures presented here will change in future. 


# Coding frequency and tools

## Coding frequency

We asked respondents "In your current role, how often do you write code to complete your work objectives?". Please note this survey is likely to have attracted many analysts with an interest in programming and so may be skewed. 

```{r}
plot <- carsurvey2::plot_freqs(tables$code_freq, "Coding frequency", "Count", n = samples$all, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$code_freq)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("coding-freq", plot, table)

```

## What people are using code for 

We asked respondents what data operations they do in their work, and whether they use code to do them. Please note the response here is "I do some or all of this by coding" and doesn't offer how much is completed with code. 

```{r}
plot <- carsurvey2::plot_stacked(tables$operations, "Count", "Data operation", n = samples$all, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$operations)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("operations", plot, table)
```

## Access to and knowledge of programming languages

Given a list of programming tools, we asked respondents to answer “Yes”, “No” or “Don’t know” for the following statements;

* This tool is available to use for my work.
* I know how to program with this tool to a level suitable for my work. 

Please note we did not set precise definitions for availability and knowledge here, as these are dependent on individual circumstances. 

## Access to coding tools

```{r}
plot <- carsurvey2::plot_stacked(tables$access, xlab = "Count", ylab = "Programming tool", n = samples$all, colour_scale = "3scale", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$access, row.names = FALSE)) %>%  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-access", plot, table)
```

## Knowledge of coding tools

```{r}
plot <- carsurvey2::plot_stacked(tables$knowledge, xlab = "Count", ylab = "Programming tool", n = samples$all, colour_scale = "3scale", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$knowledge, row.names = FALSE)) %>%  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-knowledge", plot, table)
```

## Access and knowledge gaps

Using data collected from previous questions we calculated the number of respondents who have access but no knowledge, access and knowledge, and knowledge but no access for each programming language. 

```{r}

plot <- carsurvey2::plot_stacked(tables$language_status, colour_scale = "3scale", xlab = "Count", ylab = "Programming tool", n = samples$all, font_size = 14, width = 700)

table <- kableExtra::kable_styling(knitr::kable(tables$language_status, row.names = FALSE)) %>%
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("tools-status", plot, table)

```


# Coding capability

## Change in coding ability during current role

This question was only asked of respondents with coding experience outside of their current role. This means the data does not cover those who first learned to code in their current role.

``` {r}
plot <- carsurvey2::plot_freqs(tables$ability_change, xlab = "Change in ability", ylab = "Count", n = samples$code_outside_current_role, break_q_names_col = "Ability Change", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$ability_change, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$code_outside_current_role))

carsurvey2::wrap_outputs("ability", plot, table)

```

## Where respondents learned to code

Respondents were asked whether they had coding experience outside their current role and, if so, where. 

``` {r}

plot <- carsurvey2::plot_freqs(tables$where_learned, xlab = "", ylab = "Count", n = samples$any_code_experience, break_q_names_col = "First coding experience", orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$where_learned, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$any_code_experience))

carsurvey2::wrap_outputs("first-learn", plot, table)

```


# Coding practices

We asked respondents who said they use code in their work how often they carry out various coding practices considered to be good practice. For more information on the practices presented below, please read our guidance on [Quality Assurance of Code for Analysis and Research](https://best-practice-and-impact.github.io/qa-of-code-guidance/intro.html).

## General coding practices

```{r}
plot <- carsurvey2::plot_likert(tables$coding_practices, 5, "Frequency", "", n = samples$coders, neutral_mid = FALSE, font_size = 14, height = 1000, width = 700, break_q_names_col = "Question", max_lines = 3)

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$coding_practices)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("code-prac", plot, table)

```


## Documentation

[Embedded documentation](https://best-practice-and-impact.github.io/qa-of-code-guidance/code_documentation.html) is one of the components which make up a RAP minimum viable product. Documentation is important to help others be clear on what the code is doing. 

```{r}
plot <- carsurvey2::plot_likert(tables$doc, 5, "Frequency", "", n = samples$coders, neutral_mid = FALSE, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$doc)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("doc", plot, table)

```


## Dependency management

```{r}

plot <- carsurvey2::plot_freqs(tables$dependency_management, xlab = "Use dependency management software", ylab = "count", n = samples$coders, break_q_names_col = "Use dependency management software", font_size = 14, width = 600)


table <- kableExtra::kable_styling(knitr::kable(tables$dependency_management)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("dep_management", plot, table)

```


## Reproducible workflow packages


``` {r}

plot <- carsurvey2::plot_freqs(tables$rep_workflow, xlab = "Use reproducible workflows packages", ylab = "count", n = samples$coders, break_q_names_col = "Use reproducible workflow packages", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rep_workflow)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("workflow", plot, table)

```


# RAP knowledge and opinions

We asked respondents about their knowledge of and opinions on [reproducible analytical pipelines (RAP)](https://gss.civilservice.gov.uk/reproducible-analytical-pipelines/). RAP refers to the use of practices from software engineering to make analysis more reproducible. These practices build on the advantages of writing analysis as code by ensuring increased quality, trust, efficiency, business continuity and knowledge management. The [RAP champions](https://gss.civilservice.gov.uk/about-us/champion-networks/reproducible-analytical-pipeline-rap-champions/) are a network of analysts across government who promote and support RAP development in their departments.

# Knowledge of RAP

We asked our respondents whether they had heard of RAP and what their knowledge is of their own department RAP champion.

```{r}
plot <- carsurvey2::plot_freqs(tables$rap_knowledge, "", "Count", n = samples$all, font_size = 14, orientation = "h", break_q_names_col = "RAP champion knowledge", max_lines = 3, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rap_knowledge, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$all))

carsurvey2::wrap_outputs("rap-knowledge", plot, table)

```


## Opinions on RAP

We asked respondents who had heard of RAP what there opinion was on a series of statements.


```{r}
plot <- carsurvey2::plot_likert(tables$rap_opinions, 3, "Frequency", "", n = samples$heard_of_rap, font_size = 14, height = 700, width = 700, break_q_names_col = "Question")

table <- kableExtra::kable_styling(carsurvey2::output_likert_table(tables$rap_opinions)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$heard_of_rap))

carsurvey2::wrap_outputs("rap-opinions", plot, table)

```


# RAP scores

## RAP components

The frequencies for each RAP component are derived where respondents answered “regularly” or “all the time” to the relevant questions. This graph shows the frequency of basic and advanced RAP components. “Basic” relates to the components which make up a (minimum viable product)[https://github.com/best-practice-and-impact/rap_mvp_maturity_guidance/blob/master/Reproducible-Analytical-Pipelines-MVP.md]. Advanced are practices which although not compulsory for MVP we highly recommend are done for good practice.

```{r}
plot <- carsurvey2::plot_grouped(tables$rap_components, "", "Count", n = samples$coders, orientation = "h", font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$rap_components, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("rap_comps", plot, table)

```


## Basic RAP scores

To calculate a respondent’s basic RAP score sum each of the basic rap components used regularly.

```{r}

bar_colour <- carsurvey2::get_2colour_scale(2)[2][[1]]
bar_colour <- rgb(bar_colour[1],bar_colour[2],bar_colour[3], maxColorValue = 255)

plot <- carsurvey2::plot_freqs(tables$basic_rap_scores, "Basic RAP score", "Count", bar_colour = bar_colour, n = samples$coders, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$basic_rap_scores, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("basic_score", plot, table)

```


## Advanced RAP scores

To calculate a respondent’s advanced RAP score sum each of the advanced RAP components used regularly.

```{r}

plot <- carsurvey2::plot_freqs(tables$advanced_rap_scores, "Advanced RAP score", "Count", n = samples$coders, font_size = 14, width = 600)

table <- kableExtra::kable_styling(knitr::kable(tables$advanced_rap_scores, row.names = FALSE)) %>% 
  kableExtra::add_footnote(paste0("Sample size = ", samples$coders))

carsurvey2::wrap_outputs("advanced_score", plot, table)

```
